Universelle Turingmaschine mit zwei Zuständen/Symbolen

### 2017-06-27 Kleines Studienprojekt/Eine universelle Turingmaschine mit zwei inneren Zuständen.tex
progress with the projekt-ausarbeitung

\documentclass[12pt, a4paper, twoside]{article}
\usepackage[utf8]{inputenc}
% font size could be 10pt (default), 11pt or 12 pt
% paper size coulde be letterpaper (default), legalpaper, executivepaper,
% a4paper, a5paper or b5paper
% side coulde be oneside (default) or twoside 
% columns coulde be onecolumn (default) or twocolumn
% graphics coulde be final (default) or draft 
%
% titlepage coulde be notitlepage (default) or titlepage which 
% makes an extra page for title 
% 
% paper alignment coulde be portrait (default) or landscape 
%
% equations coulde be 
%   default number of the equation on the rigth and equation centered 
%   leqno number on the left and equation centered 
%   fleqn number on the rigth and  equation on the left side
%	
\author{Sven Fiergolla}
\title{Universelle Turingmaschine mit zwei Zuständen/Symbolen}
\date{\today}

@@

\subsection{Formale Definition der Turingmaschine}
Formal wir die Turingmaschine als Septupel $\mathbf{ M = (Q,\Sigma,\Gamma,\sigma} $

\subsubsection{even more introduction}
come to the point \ldots

@@

\section{Documentclasses} \label{documentclasses}

>>>>

\documentclass[12pt, a4paper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsrefs}

% font size could be 10pt (default), 11pt or 12 pt
% paper size coulde be letterpaper (default), legalpaper, executivepaper,
% a4paper, a5paper or b5paper
% side coulde be oneside (default) or twoside 
% columns coulde be onecolumn (default) or twocolumn
% graphics coulde be final (default) or draft 
%
% titlepage coulde be notitlepage (default) or titlepage which 
% makes an extra page for title 
% 
% paper alignment coulde be portrait (default) or landscape 
%
% equations coulde be 
%   default number of the equation on the rigth and equation centered 
%   leqno number on the left and equation centered 
%   fleqn number on the rigth and  equation on the left side
%	
\author{Sven Fiergolla}
\title{Universelle Turingmaschine mit zwei Zuständen/Symbolen}
\date{\today}

@@

\subsection{Formale Definition der Turingmaschine}
Formal wir die Turingmaschine als Septupel $\mathbf{ M = (Q,\Sigma,\Gamma,q_0,\delta,\Square,F)} $

\subsection{universelle Turingmaschinen}
come to the point \ldots

@@

\section{Universelle TM mit nur zwei Zuständen}

\section{TM mit einem Zustand niemals universell}

\section{Universelle TM mit zwei Symbolen}

\section{Fazit}
